TBD

### 2021-02-25 outputs/paper/paper.Rmd
Add captions to figures

```{r Q1, echo = FALSE, message=FALSE}
ggplot(data = all_simulated_dataset, mapping = aes (x = Q1, fill = type)) +
  geom_bar() + coord_flip() +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  labs(fill = "Condition", title = "Location of restaurants")
```

```{r Q2, echo = FALSE, message = FALSE}
### How would you best describe the scale of your restaurant? (in terms of space and seating capacity)
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "
ggplot(data = all_simulated_dataset, mapping = aes (x = Q2, fill = type)) +
    geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Seating Capacity",
       y = "# of Restaurants",
       fill = "Condition",
       title = "Scale of restaurant (space/[eseating capacity)") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

>>>>

```{r Q1, echo = FALSE, message = FALSE, fig.cap = "Location of restaurants by borough"}
ggplot(data = all_simulated_dataset, mapping = aes (x = Q1, fill = type)) +
  geom_bar() + coord_flip() +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  labs(fill = "Condition", title = "Location of restaurants")
```

```{r Q2, echo = FALSE, message = FALSE, fig.cap = "Scale of restaurant in terms of space and seating capacity"}
### How would you best describe the scale of your restaurant? (in terms of space and seating capacity)
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "
ggplot(data = all_simulated_dataset, mapping = aes (x = Q2, fill = type)) +
    geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Seating Capacity",
       y = "# of Restaurants",
       fill = "Condition",
       title = "Scale of restaurant") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```
